State of the Practice for Lattice Boltzmann Method Software

### 2022-04-23 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
reviewed Section 11

Our threats to validity categories come from an analysis of software engineering
secondary studies by \citet{AmpatzoglouEtAl2019}.  We use the classification of
\citep{AmpatzoglouEtAl2019} because studying a collection of software is a form
of secondary study, where a secondary study analyzes the data from a set of
primary studies.  A common example of a secondary study is a systematic
literature review.  Our methodology is essentially a systematic software review
-- the primary studies are the software, and our work collects and analyzes
these primary studies.

@@

\begin{itemize}
\item In our methodology the manual measures are done by one individual for all
packages. The measures may be influenced by the graders abilities, experience,
and biases.  
\item Completing the manual measures of all packages took place over several
months. During this time the contents of the software repositories may change
and the reviewer's judgment may drift.
\end{itemize}

@@

\begin{itemize}
\item We may have missed a relevant software package in our search for LBM
software packages (Section~\ref{identifysoftware}).
\item A temporal gap exists between the manual measurement of Musubi and the
measurement of all other packages (Section~\ref{identifysoftware}). This gap
caused a mismatch between the time of manual and automated data collection
(Section~\ref{repmetrics}), since we updated the automated measures (like the
number of files, LOC, etc.) when Musubi was added.
\item Our interviews were with a relatively small sample of four LBM developers.
The pain points they expressed may not be representative of others in the
community.
\item In our manual measures of the software repositories some data may not have
been measured due to technology issues like broken links. This issue arose with
the measurement of Palabos, which had a broken link to its user manual, as noted
in Section~\ref{Sec_CompareArtifacts}. 
\item Our methodology assumes that artifacts will be present in the repositories
to approach used for software development.  However, not all activities will
necessarily leave a trace in the repositories. For instance, the use of unit
testing and CI was mentioned in the artifacts of only three (ESPResSo, Ludwig,
Musubi) packages (Section~\ref{SecSurfCorrectAndVerifiab}). However, interviews
suggested a more frequent use of both unit testing and CI. For example, OpenLB,
pyLBM, and TCLB use such methods during development despite this not being
explicit from an analysis of the material available online.
\end{itemize}

Although we found that unit testing and CI were used more often than the
repository artifacts suggested, we did not change the manual measurement
results.  Given that we could not interview a representative for every project,
we left the data as collected to keep our measures consistent.  Moreover, CI and
unit testing done in private should not be counted as equivalent to the public
versions we detected.  When CI and unit testing are done outside the public
repository, they are not as effective, since they are not available for others
to inspect and reproduce.

>>>>

Our threats to validity categories come from an analysis of software engineering
secondary studies by \citet{AmpatzoglouEtAl2019}.  We use the classification of
\citet{AmpatzoglouEtAl2019} because studying a collection of software is a form
of secondary study, where a secondary study analyzes the data from a set of
primary studies.  A common example of a secondary study is a systematic
literature review.  Our methodology is essentially a systematic software review
-- the primary studies are the software, and our work collects and analyzes
these primary studies.

@@

\begin{itemize}
\item In our methodology, the manual measures are done by one individual for all
packages. The measures may be influenced by the grader's abilities, experience,
and biases.  
\item Completing the manual measures of all packages took place over several
months. During this time the contents of the software repositories may change
and the reviewer's judgment may drift.
\end{itemize}

@@

\begin{itemize}
\item We may have missed a relevant software package in our search for LBM
software packages (Section~\ref{identifysoftware}).
\item A temporal gap exists between the manual measurement of Musubi and the
measurement of all other packages (Section~\ref{identifysoftware}). This gap
caused a mismatch between the time of manual and automated data collection
(Section~\ref{repmetrics}), since we updated the automated measures (like the
number of files, LOC, etc.) when Musubi was added.
\item Our interviews were with a relatively small sample of four LBM developers.
The pain points they expressed may not be representative of others in the
community.
\item In our manual measures of the software repositories, some data may not have
been measured due to technology issues like broken links. This issue arose with
the measurement of Palabos, which had a broken link to its user manual, as noted
in Section~\ref{Sec_CompareArtifacts}. 
\item Our methodology assumes that artifacts will be present in the repositories
to approach used for software development.  However, not all activities will
necessarily leave a trace in the repositories. For instance, the use of unit
testing and CI was mentioned in the artifacts of only three (ESPResSo, Ludwig,
Musubi) packages (Section~\ref{SecSurfCorrectAndVerifiab}). However, interviews
suggested a more frequent use of both unit testing and CI. For example, OpenLB,
pyLBM, and TCLB use such methods during development despite this not being
explicit from an analysis of the material available online.
\end{itemize}

Although we found that unit testing and CI were used more often than the
repository artifacts suggested, we did not change the manual measurement
results.  Given that we could not interview a representative for every project,
we left the data as collected to keep our measures consistent.  Moreover, CI and
unit testing done in private should not be counted as equivalent to the public
versions we detected.  When CI and unit testing are done outside the public
repository, they are not as effective since they are not available for others
to inspect and reproduce.
